\vspace{-2cm}A generative model for urban firm networks

### 2021-05-28 main.tex
.

The communities reflect characteristic socio-cultural structures and cross-border economic ties throughout Europe. Cities in France, Belgium and Luxembourg belong to the same cluster as they share French as a common business language, but also cross-border tax arrangements creating easier economic interactions \cite{DecovilleDurand2019}. The same socio-cultural proximity effect is seen in cities of the United Kingdom and Ireland, and those of Sweden, Finland, Estonia, Latvia and Lithuania. The cluster composed of Dutch and Polish cities is justified by the fact that firms from the Netherlands are among the first foreign owners of polish firms since 2010 \cite{2020Zdanowska}. The cluster including cities in Germany, Czech Republic, Austria, Slovakia, Hungary and partly in Romania, find its origin in the dependence of the Central and Eastern European economies on German and Austrian large companies mostly from the automotive sector (i.e. Audi, Volkswagen). In addition, all cities of the later cluster have in common to be at the intersection of a very important freight transport route in Europe from Germany to Turkey \cite{Zdanowska2017}. 
%%%%%%%%%%%%%%
\begin{figure}
    \begin{center}
    \includegraphics[width=\linewidth]{figures/Fig2.png}
    \end{center}
    \vspace{2cm}
    \caption{{\bf Map of network communities obtained by modularity maximisation.} The area of circles gives the turnover within the Functional Urban Area, and color the community it belongs to. Urban Areas in communities of size smaller than 3 were not colored for readability.}
    \label{fig:fig2}
    % TODO redo map with open resources (see editor request) https://www.naturalearthdata.com/downloads/110m-cultural-vectors/
\end{figure}
%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%
\begin{table}[!ht]
\begin{adjustwidth}{-1in}{0in}
\caption{{\bf Statistical models.} Ordinary Least Square estimations of statistical models explaining $\log(w_{ij})$ (standard errors in parenthesis). ***, ** and * respectively indicate 0.01, 0.05 and 0.1 levels of significance. For the fixed effect by origin-destination pairs of countries, the proportion of significant coefficients is attributed (where $p<0.1$). Models (1) to (4) are ordinary least square models, while model (5) is a Poisson generalized linear model with logarithmic link. We compare model performance using $R^2$, Mean Square Error, and Akaike Information Criterion. For the Poisson model (model 5), AIC is not given as it is not comparable. \label{tab:reg}}
\medskip
\begin{tabular}{|l|c|c|c|c|c|}
\hline
Model  & (1) & (2) & (3) & (4) & (5) \\ 
\hline
$\log(d_{ij})$ &      -0.06** (0.03) &   -0.11** (0.05)  & -0.41*** (0.02)  & -0.35*** (0.04)  &  -0.26*** ($5\cdot 10^{-6}$) \\
$\log(T_i)$ &   &   & 0.56*** (0.01) &  0.56*** (0.01) & 0.79*** ($2\cdot 10^{-6}$) \\
$\log(T_j)$ &     &   & 0.39*** (0.01) &  0.39*** (0.01) & 0.66***  ($1.5\cdot 10^{-6}$) \\
$\log(s_{ij})$ &     &   &  &  0.19*** (0.07) & 0.53*** ($9\cdot 10^{-6}$)  \\
Countries &    &  28.3\% &   &  26.5\% & 100\% \\
\hline
$R^2$ &       0.00059   &  0.17 & 0.21 &  0.31  &  0.56 \\
MSE & 7.75 & 6.84 & 6.10 & 5.33 & 8.72 \\
AIC &        44304   &  43578  &  42131  & 41917 &   \\
\hline
\end{tabular}
\end{adjustwidth}
\end{table}
%%%%%%%%%%%%%

>>>>

The communities reflect characteristic socio-cultural structures and cross-border economic ties throughout Europe. Cities in France, Belgium and Luxembourg belong to the same cluster as they share French as a common business language, but also cross-border tax arrangements creating easier economic interactions \cite{DecovilleDurand2019}. The same socio-cultural proximity effect is seen in cities of the United Kingdom and Ireland, and those of Sweden, Finland, Estonia, Latvia and Lithuania. The cluster composed of Dutch and Polish cities is justified by the fact that firms from the Netherlands are among the first foreign owners of polish firms since 2010 \cite{2020Zdanowska}. The cluster including cities in Germany, Czech Republic, Austria, Slovakia, Hungary and partly in Romania, find its origin in the dependence of the Central and Eastern European economies on German and Austrian large companies mostly from the automotive sector (i.e. Audi, Volkswagen). In addition, all cities of the later cluster have in common to be at the intersection of a very important freight transport route in Europe from Germany to Turkey \cite{Zdanowska2017}. 
%%%%%%%%%%%%%%
\begin{figure}
    \begin{center}
    \includegraphics[width=\linewidth]{figures/Fig2.png}
    \end{center}
    \vspace{2cm}
    \caption{{\bf Map of network communities obtained by modularity maximisation.} The area of circles gives the turnover within the Functional Urban Area, and colour the community it belongs to. Urban Areas in communities of size smaller than 3 were not coloured for readability.}
    \label{fig:fig2}
    % TODO redo map with open resources (see editor request) https://www.naturalearthdata.com/downloads/110m-cultural-vectors/
\end{figure}
%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%
\begin{table}[!ht]
\begin{adjustwidth}{-1in}{0in}
\caption{{\bf Statistical models.} Ordinary Least Square estimations of statistical models explaining $\log(w_{ij})$ (standard errors in parenthesis). ***, ** and * respectively indicate 0.01, 0.05 and 0.1 levels of significance. For the fixed effect by origin-destination pairs of countries, the proportion of significant coefficients is attributed (where $p<0.1$). Models (1) to (4) are ordinary least square models, while model (5) is a Poisson generalised linear model with logarithmic link. We compare model performance using $R^2$, Mean Square Error, and Akaike Information Criterion. For the Poisson model (model 5), AIC is not given as it is not comparable. \label{tab:reg}}
\medskip
\begin{tabular}{|l|c|c|c|c|c|}
\hline
Model  & (1) & (2) & (3) & (4) & (5) \\ 
\hline
$\log(d_{ij})$ &      -0.06** (0.03) &   -0.11** (0.05)  & -0.41*** (0.02)  & -0.35*** (0.04)  &  -0.26*** ($5\cdot 10^{-6}$) \\
$\log(T_i)$ &   &   & 0.56*** (0.01) &  0.56*** (0.01) & 0.79*** ($2\cdot 10^{-6}$) \\
$\log(T_j)$ &     &   & 0.39*** (0.01) &  0.39*** (0.01) & 0.66***  ($1.5\cdot 10^{-6}$) \\
$\log(s_{ij})$ &     &   &  &  0.19*** (0.07) & 0.53*** ($9\cdot 10^{-6}$)  \\
Countries &    &  28.3\% &   &  26.5\% & 100\% \\
\hline
$R^2$ &       0.00059   &  0.17 & 0.21 &  0.31  &  0.56 \\
MSE & 7.75 & 6.84 & 6.10 & 5.33 & 8.72 \\
AIC &        44304   &  43578  &  42131  & 41917 &   \\
\hline
\end{tabular}
\end{adjustwidth}
\end{table}
%%%%%%%%%%%%%
